Discussion

### 2023-04-11 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
removed comment (we talked about suppression)
added "positive"

The present Registered Report was designed to assess whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies distraction, distancing, and suppression.
We adapted Westbrook et al.'s[-@Westbrook2013] Cognitive Effort Discounting paradigm in a way that allows SVs to be determined for tasks without objective difficulty order. 
The new paradigm was tested on an *n*-back task[@ZernaScheffel2022] and a classic ER paradigm.
The latter was the goal of the present study and completed by $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants. 
As expected, the use of ER strategies was associated with reduced subjective and physiological arousal.
This finding is in line with previous meta-analytic findings indicating the effectiveness of ER strategies, both on subjective as well as physiological levels[@Webb2012;@Zaehringer2020]. <!-- evtl. Einwand warum Suppression am erfolgreichsten war --> 
Furthermore, we found higher levels of subjective cognitive effort for all ER strategies compared to active viewing. 
This allows us to replicate previous findings from our research group and show that strategy use is associated with cognitive effort[@Scheffel2021].
Both measures also showed high variability between individuals.
Taken together, this means that the ER strategies had the intended effect on the participants: Individuals were able to effectively reduce subjective and physiological responding at the expense of cognitive effort.
It was nevertheless surprising that the strategy suppression showed on average and descriptively the lowest *corrugator* activity, the lowest effort ratings and the highest utility ratings. 
In the case of the EMG measurement, this could be due to the fact that the result of the implementation of the instructions ("Maintain a neutral facial expression") is measured directly. 
The direct instruction also reduces the complexity of the generation process, which is why the required effort is the lowest.
By comparison, distancing increases the complexity, because it requires an impersonal reappraisal of the stimulus.
Ultimately, the immediacy and simplicity are then expressed in terms of greater subjective utility of the strategy. 
In addition, one receives relatively direct feedback from one's own facial muscle activity as to how well the strategy suppression has been implemented.
In the case of the strategies distraction and distancing, a more detailed evaluation of internal states must take place in order to assess their utility, which again requires more effort.
Since the manipulation checks were successful, the subjective and physiological measures were likely to be meaningful in influencing the individual SVs.

Almost all participants showed an absolute preference for a particular strategy, indicated by an SV of 1. 
We also found a wide range of SVs (between `r papaja::apa_num(min(data_SV$sv), digits = 3)` and `r papaja::apa_num(max(data_SV$sv))`), suggesting that individuals have varying degrees of strategy preference.
There was a significant relationship between SVs and strategy choice. 
Overly frequent, persons chose the strategy for which the highest subjective value had been determined before, supporting hypothesis H7.
We also found associations between individual SVs and various predictors.
Subjective effort, utility, and *corrugator* muscle activity significantly predicted individual SVs.
Contrary to our hypothesis H6, utility and not effort was the best predictor for individual SVs, explaining `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.
However, since individual SVs did not show associations with self-reported ER flexibility, we found no evidence for hypothesis H7.
In a subsequent exploratory analyses, we found associations between individual SVs and self-control.
This is consistent with the literature, which has already reported correlations between self-control and demand avoidance[@Kool2013].
However, we did not find an association between NFC and SVs. 
This is in contrast to the literature, which has reported correlations between NFC, effort discounting and demand avoidance[@ZernaScheffel2022;@Westbrook2013].
However, these were all cognitive tasks. The role of NFC in affective tasks is not yet known.

>>>>

The present Registered Report was designed to assess whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies distraction, distancing, and suppression.
We adapted Westbrook et al.'s[-@Westbrook2013] Cognitive Effort Discounting paradigm in a way that allows SVs to be determined for tasks without objective difficulty order. 
The new paradigm was tested on an *n*-back task[@ZernaScheffel2022] and a classic ER paradigm.
The latter was the goal of the present study and completed by $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants. 
As expected, the use of ER strategies was associated with reduced subjective and physiological arousal.
This finding is in line with previous meta-analytic findings indicating the effectiveness of ER strategies, both on subjective as well as physiological levels[@Webb2012;@Zaehringer2020].
Furthermore, we found higher levels of subjective cognitive effort for all ER strategies compared to active viewing. 
This allows us to replicate previous findings from our research group and show that strategy use is associated with cognitive effort[@Scheffel2021].
Both measures also showed high variability between individuals.
Taken together, this means that the ER strategies had the intended effect on the participants: Individuals were able to effectively reduce subjective and physiological responding at the expense of cognitive effort.
It was nevertheless surprising that the strategy suppression showed on average and descriptively the lowest *corrugator* activity, the lowest effort ratings and the highest utility ratings. 
In the case of the EMG measurement, this could be due to the fact that the result of the implementation of the instructions ("Maintain a neutral facial expression") is measured directly. 
The direct instruction also reduces the complexity of the generation process, which is why the required effort is the lowest.
By comparison, distancing increases the complexity, because it requires an impersonal reappraisal of the stimulus.
Ultimately, the immediacy and simplicity are then expressed in terms of greater subjective utility of the strategy. 
In addition, one receives relatively direct feedback from one's own facial muscle activity as to how well the strategy suppression has been implemented.
In the case of the strategies distraction and distancing, a more detailed evaluation of internal states must take place in order to assess their utility, which again requires more effort.
Since the manipulation checks were successful, the subjective and physiological measures were likely to be meaningful in influencing the individual SVs.

Almost all participants showed an absolute preference for a particular strategy, indicated by an SV of 1. 
We also found a wide range of SVs (between `r papaja::apa_num(min(data_SV$sv), digits = 3)` and `r papaja::apa_num(max(data_SV$sv))`), suggesting that individuals have varying degrees of strategy preference.
There was a significant relationship between SVs and strategy choice. 
Overly frequent, persons chose the strategy for which the highest subjective value had been determined before, supporting hypothesis H7.
We also found associations between individual SVs and various predictors.
Subjective effort, utility, and *corrugator* muscle activity significantly predicted individual SVs.
Contrary to our hypothesis H6, utility and not effort was the best predictor for individual SVs, explaining `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.
However, since individual SVs did not show associations with self-reported ER flexibility, we found no evidence for hypothesis H7.
In a subsequent exploratory analyses, we found a positive association between individual SVs and self-control.
This is consistent with the literature, which has already reported correlations between self-control and demand avoidance[@Kool2013].
However, we did not find an association between NFC and SVs. 
This is in contrast to the literature, which has reported correlations between NFC, effort discounting and demand avoidance[@ZernaScheffel2022;@Westbrook2013].
However, these were all cognitive tasks. The role of NFC in affective tasks is not yet known.
